\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-07 metatheory-condensed.tex
coqimpl
related work on EP
Nada's comment

We contribute \TT, a core type theory that incorporates the core elements
of \underline{f}a\underline{m}i\underline{l}y polymorphism into
\underline{M}artin-\underline{L}öf dependent \underline{t}ype \underline{t}heory~\cite{martin1982constructive},
while maintaining consistency and canonicity.

@@

We illustrate this with \cref{fig:stlc-linkage-typing}.
On the left is code excerpted from \cref{fig:stlc-mechanized}, and on the right
is how the corresponding fields are modeled and typed in \TT.
%
$\lkg_i$ is the linkage that adds the $i$-th field~$t_i$ with the typing
$\goodTerm{%
\tikzmarkin[disable rounded corners=true,set fill color=A-color,set border color=A-color]{A-i}(-0.02,-0.10)(-0.02,0.28)
A_i%
\tikzmarkend{A-i}%
}{%
\tikzmarkin[disable rounded corners=true,set fill color=t-color,set border color=t-color]{t-i}(-0.02,-0.10)(-0.02,0.28)%
t_i%
\tikzmarkend{t-i}%
}{%
\tikzmarkin[disable rounded corners=true,set fill color=T-color,set border color=T-color]{T-i}(-0.02,-0.10)(-0.02,0.28)%
T_i%
\tikzmarkend{T-i}%
}$.
%
For readability, we feel free to use a notation with explicit names
in this typing judgment:
we name the context as $\mathit{self}$ (cf.~\cref{fig:stlc-compiled})
and feel free to write its type~$A_i$, which is a dependent tuple type, as a
dependent record type with labels.
%
\begin{itemize}
  [leftmargin=4ex]
  %[labelsep=*,leftmargin=1pc]

@@

\item
Similarly, $\wsig_{\texttt{tm}}$ is exposed to the typing context of
$t_{10}$, which models the recursive function \lsti{subst} by invoking
the recursor $\Wrec{\wsig_{\texttt{tm}}}{\cDot}{\cDot}$.
%
Other fields automatically generated by the plugin, such as partial
recursors and various propositional equalities, can also be modeled in
this way by invoking $\texttt{Wrec}$.

@@

\newpage

@@

\newcommand{\denotesT}[1]{{{\llbracket {#1} \rrbracket}_T}}
\newcommand{\Sigr}[2]{{ "Sig"^r~{#1}~{#2} }}

>>>>

We contribute \TT, a core type theory that incorporates the core elements
of \underline{f}a\underline{m}i\underline{l}y polymorphism into
\underline{M}artin-\underline{L}öf dependent \underline{t}ype \underline{t}heory~\cite{martin1982constructive},
while maintaining consistency and canonicity.\NA{maybe you can give an overview of the salient points of the design and what they're trying to achieve? What is the core aspect modeled by the theory?}

@@

We illustrate this with \cref{fig:stlc-linkage-typing}.
On the left is code excerpted from \cref{fig:stlc-mechanized}, and on the right
is how the corresponding fields are modeled and typed in \TT.
%
$\lkg_i$ is the linkage that adds the $i$-th field~$t_i$ with the typing
$\goodTerm{%
\tikzmarkin[disable rounded corners=true,set fill color=A-color,set border color=A-color]{A-i}(-0.02,-0.10)(-0.02,0.28)
A_i%
\tikzmarkend{A-i}%
}{%
\tikzmarkin[disable rounded corners=true,set fill color=t-color,set border color=t-color]{t-i}(-0.02,-0.10)(-0.02,0.28)%
t_i%
\tikzmarkend{t-i}%
}{%
\tikzmarkin[disable rounded corners=true,set fill color=T-color,set border color=T-color]{T-i}(-0.02,-0.10)(-0.02,0.28)%
T_i%
\tikzmarkend{T-i}%
}$.
%
For readability, we feel free to use a notation with explicit names
in this typing judgment:
we name the context as $\mathit{self}$ (cf.~\cref{fig:stlc-compiled})
and feel free to write its type~$A_i$, which is a dependent tuple type, as a
dependent record type with labels.
%
\begin{itemize}
% [leftmargin=4ex,itemsep=.5ex]
  [labelsep=*,leftmargin=1pc,itemsep=3pt]

@@

\item
Similarly, $\wsig_{\texttt{tm}}$ is exposed to the typing context of
$t_{10}$, which models the recursive function \lsti{subst} by invoking
the recursor $\Wrec{\wsig_{\texttt{tm}}}{\cDot}{\cDot}$.
%
Partial recursors automatically generated by the plugin
can also be modeled in this way by invoking $\texttt{Wrec}$.

@@

\ifShowOldWriting
\newpage

@@
